BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for Realistic BPMN Models

### 2024-06-24 main.tex
gitignore
Add authors

%%
%% One can fix some overfills
\sloppy

@@

\title{Instantaneous, Comprehensible, and Fixable Soundness Checking of Realistic BPMN Models}

\author[1]{Tim Kräuter}[
email=tkra@hvl.no
]
\address[1]{Western Norway University of Applied Sciences, Bergen, Norway}

\begin{abstract}
  TBD
\end{abstract}

@@

\section{Introduction}
\cite{krauterFormalizationAnalysisBPMN2023}

\section{Innovations?}

@@

>>>>

%%
%% One can fix some overfills
% \sloppy

% This was used to mitigate some warnings
\usepackage[T1]{fontenc}
\usepackage{lmodern}

@@

% TODO: Rename Rust BPMN Analyzer to BPMN Analyzer 2.0 on my website and maybe somewhere on GitHub.
\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for Realistic BPMN Models}

\author[1]{Tim Kräuter}
[email=tkra@hvl.no]
\author[1]{Patrick Stünkel}
[email=patrick.stuenkel@hvl.no]
\author[1]{Adrian Rutle}
[email=aru@hvl.no]
\author[1]{Yngve Lamo}
[email=yla@hvl.no]
\author[2,1]{Harald König}
[email=harald.koenig@fhdw.de]
\address[1]{Western Norway University of Applied Sciences, Bergen, Norway}
\address[2]{FHDW Hannover, Germany}

\begin{abstract}
  The tool is available online.
\end{abstract}

@@

\section{Introduction}
The tool is available online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=MxXbNUl6IjE}}.
% Why is it significant for the BPM field?

\section{Innovations?} % Main tool description and showing the innovations
Three main innovations of the tool:
% Instantaneous
% Comprehensible
% Fixable

\section{Maturity of the tool}
% Scalability tests (instantaneous)
Improves upon our previous BPMN Analyzer tool~\cite{krauterFormalizationAnalysisBPMN2023}.
% bpmn.io forum link/mention

@@

\section{Related work?}

\section{Conclusion \& future work}
